---
title: "p8105_hw6_WZ2591"
author: "Wenyu Zhang"
date: "12/1/2021"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
## Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = factor(babysex, 
                     levels = c("1", 
                                "2")),
    frace = factor(frace, 
                   levels = c("1", 
                              "2", 
                              "3", 
                              "4", 
                              "8", 
                              "9")),
    malform = factor(malform, 
                     levels = c("0", 
                                "1")),
    mrace = factor(mrace, 
                   levels = c("1", 
                              "2", 
                              "3", 
                              "4", 
                              "8"))
  )

sum(is.na(birthweight_df))
```

There is no NA data in this dataset

## Propose a regression model for birthweight

```{r}
model_fit = lm(bwt ~ babysex + bhead + blength + gaweeks, data = birthweight_df)

model_fit %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

summary(model_fit)
```

```{r}
modelr::add_residuals(birthweight_df, model_fit)
modelr::add_predictions(birthweight_df, model_fit)
```

```{r}
birthweight_df %>% 
  add_predictions(model_fit) %>% 
  add_residuals(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5, size = 0.5) +
  labs(x = "Predicted values", 
       y = "Residual",
       title = "plot of model residuals against fitted values")

```

## Describe your modeling process

1. the predictors I choose are `babysex`, `bhead`, `blength` and `gaweeks`. 

2. Then I build a linear regression model for baby’s birth weight with the influences of baby’s sex, baby’s head circumference at birth, baby’s length at birth and gestational age in weeks.

3. According to the plot, most of the points are between the area from 2000 to 4000.

## Compare your model to two others:
### One using length at birth and gestational age as predictors (main effects only)

```{r}
model_fit2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)

model_fit2 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

summary(model_fit2)
```

### One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
model_fit3 = lm(bwt ~ bhead * blength * babysex, data = birthweight_df)

model_fit3 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

summary(model_fit3)
```

## Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
cv_df = 
    crossv_mc(birthweight_df, 100) %>% 
    mutate(
      train = map(train, as_tibble),
      test = map(test, as_tibble)
      )
```

```{r, warning=FALSE}
cv_df =
  cv_df %>% 
  mutate(
    model_fit = map(train, ~lm(bwt ~ babysex + bhead + blength + gaweeks, data = .x)),
    model_fit1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_fit2 = map(train, ~gam(bwt ~ bhead * blength * babysex, data = .x))
    ) %>% 
  mutate(
    rmse_model_fit = map2_dbl(model_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_fit1 = map2_dbl(model_fit1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_fit2 = map2_dbl(model_fit2, .y = test, ~rmse(model = .x, data = .y))
  )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```
`model_fit` and `model_fit2` have the lowest rmse, so they are more accurate.
 
# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Distribution of $log(\hat{\beta}_0 \ast \hat{\beta}_1)$

```{r}
log_df = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(.id, results) %>% 
  unnest(results) %>% 
  mutate(term = 
           case_when(
             term == "(Intercept)" ~ "beta0",
             term == "tmin" ~ "beta1"
             )) 
```

```{r}
log_clean_df = 
  log_df %>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate) %>%
  mutate(log_beta = log(beta0 * beta1))
```

```{r}
log_clean_plot = 
  log_clean_df %>%
  ggplot(aes(x = log_beta)) + 
  geom_density() +
  labs(x = "log estimate",
       y = "Density",
       title = "distribution of log estimatie")  

log_clean_plot
```

## 95% confidence interval for $log(\hat{\beta}_0 \ast \hat{\beta}_1)$

```{r}
log_clean_df %>% 
  summarize(
    ci_lower = quantile(log_beta, 0.025), 
    ci_upper = quantile(log_beta, 0.975)) %>% 
  knitr::kable(digits = 3)
```

## Distribution of $\hat{r}^2$

```{r}
rsquared_df = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results_glance = map(models, broom::glance)) %>% 
  select(.id, results_glance) %>% 
  unnest(results_glance)
```

```{r}
rsquared_clean_df = 
  rsquared_df %>% 
  select(.id, r.squared)
```

```{r}
rsquared_clean_plot = 
  rsquared_clean_df %>%
  ggplot(aes(x = r.squared)) + 
  geom_density() +
  labs(x = "r squared",
       y = "density",
       title = "distribution of r squared estimatie")  

rsquared_clean_plot
```

## 95% confidence interval for $\hat{r}^2$

```{r}
rsquared_clean_df %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) %>% 
  knitr::kable(digits = 3)
```

